---
title: "Reproducible Document"
author: "rostools"
format: html
---

```{r setup}
#| message: false #tells system to not inlude the messages in the Render-file (default is always true)
#| warning: false

library(tidyverse)

post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv")) # using csv2 because the data is separated with ;

small_post_meal_data <- select(post_meal_data, id, Age, BMI, Group, auc_pg, auc_ins, glykemi) # creates a new dataframe from the original large dataframe with the given columns

tidier_post_meal_data <- small_post_meal_data %>%
  rename(
    auc_glucose = auc_pg,
    auc_insulin = auc_ins
  ) %>%
  filter(glykemi == 0) %>%
  select(-glykemi)
```

## About me

-   Hanna Mandrup
-   CBMR, University of Copenhagen

I am currently employed at the **Hansen Group** working with *SLD*

## Simple code

```{r}
3 * 3
```



## Writing R code

2 + 2

```{r}
2 + 2
```


## Testing for Git
hello

## Showing the data

```{r}
post_meal_data # shows data nicely in a table

glimpse(post_meal_data) # shows data more as a list with columns going down
```

## Plot one continuous variable

```{r}
#| fig-cap: "Ditribution of BMI"
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```
See @fig-bmi-histo --> #This gives you a reference to the figure because a label was added to it

## Exercise: discrete plots

```{r}
#| fig-cap: "Group count"
#| label: fig-group-bar
ggplot(post_meal_data, aes(x = Group)) +
  geom_bar()
```

See @fig-group-bar above for a cool plot!

## Plotting two discrete variables

```{r}
ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge()) # position_dodge splitd the bar plot so it's not stacked
```
## Side by side plot

```{r fig-bmi-glycemia}
#| fig-cap: "BMI and glycemia, side by side"
#| fig-subcap:
#|  - "Distribution of BMI"
#|  - "Number of those with glycemia"
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

## Plotting two continuous variables

```{r}
#| fig.cap: "Scatterplot of BMI and the area under the curve for glucose"
#| fig.label: "fig-bmi-auc-pg"
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```

## Selecting data

```{r}
select(post_meal_data, Age)

select(post_meal_data, Age, BMI, Weight)

select(post_meal_data, -Group) # Takes all columns except 'Group' because it starts with '-'

select(post_meal_data, starts_with("PG")) # Shows all columns starting with PG

select(post_meal_data, ends_with("DXA")) # Shows all columns ending with DXA

select(post_meal_data, contains("0")) # Shows all columns where a 0 is present somewhere in the column-name
```

## Renaming columns

```{r}
small_post_meal_data %>%
  rename(
    auc_glucose = auc_pg,
    auc_insulin = auc_ins
  )
```

## Select and rename tasks
```{r}
# Task 1.
post_meal_data |>
  select(contains("OGTT"))

# Task 2.
post_meal_data |>
  select(contains(".."), -contains("..."))

# Task 3.
post_meal_data |>
  rename(
    P.Glucose.minus5.OGTT = P.Glucose..5.OGTT,
    Insulin.minus5.OGTT.X = Insulin..5.OGTT.X
  )

# Task 4.

basic_info <- select(post_meal_data, id, BMI, Length, Weight, Age) %>%
  rename(Height = Length)
```

## Filtering data

```{r}
small_post_meal_data %>%
  filter(glykemi == 1)

small_post_meal_data %>%
  filter(BMI >= 25)

small_post_meal_data %>%
  filter(Group == "CTR")

small_post_meal_data %>%
  filter(Group == "CTR" | BMI >= 25)
```
