---
title: "Reproducible Document"
author: "rostools"
format: html
---

```{r setup}
#| message: false
#| warning: false

library(tidyverse)

post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv"))
```

## About me

-   Hanna Mandrup
-   CBMR, University of Copenhagen

I am currently employed at the **Hansen Group** working with *SLD*

## Simple code

```{r}
3 * 3
```



## Writing R code

2 + 2

```{r}
2 + 2
```


## Testing for Git
hello

## Showing the data

```{r}
post_meal_data # shows data nicely in a table

glimpse(post_meal_data) # shows data more as a list with columns going down
```

## Plot one continuous variable

```{r}
#| fig-cap: "Ditribution of BMI"
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```
See @fig-bmi-histo --> #This gives you a reference to the figure because a label was added to it

## Exercise: discrete plots

```{r}
#| fig-cap: "Group count"
#| label: fig-group-bar
ggplot(post_meal_data, aes(x = Group)) +
  geom_bar()
```

See @fig-group-bar above for a cool plot!

## Plotting two discrete variables

```{r}
ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge()) # position_dodge splitd the bar plot so it's not stacked
```
## Side by side plot

```{r fig-bmi-glycemia}
#| fig-cap: "BMI and glycemia, side by side"
#| fig-subcap:
#|  - "Distribution of BMI"
#|  - "Number of those with glycemia"
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

## Plotting two continuous variables

```{r}
#| fig.cap: "Scatterplot of BMI and the area under the curve for glucose"
#| fig.label: "fig-bmi-auc-pg"
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```

